Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-01-22 cordillera-cycle.tex
Rev. Jarosch: remove "SSA as a sliding law".

      Ice sheet dynamics are typically modelled using a~combination of
      internal deformation and basal sliding. PISM is a~shallow ice sheet
      model, which implies that the balance of stresses is approximated
      based on their predominant components. The Shallow Shelf Approximation
      (SSA) is used as a ``sliding law'' for the Shallow Ice Approximation
      (SIA) by adding velocity solutions of the two approximations
      \citep[Eqs.~7--9 and 15]{Bueler.Brown.2009, Winkelmann.etal.2011}.

>>>>

      Ice sheet dynamics are typically modelled using a~combination of
      internal deformation and basal sliding. PISM is a~shallow ice sheet
      model, which implies that the balance of stresses is approximated
      based on their predominant components. The Shallow Shelf Approximation
      (SSA) is combined with the Shallow Ice Approximation
      (SIA) by adding velocity solutions of the two approximations
      \citep[Eqs.~7--9 and 15]{Winkelmann.etal.2011}.
